Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-10-05 main.tex
Couple of typos (Grammarly plugin ran finally)

Recalling Assumption \ref{assum:measurement_size}, modified measurement noise resembles a Gaussian distribution when measurements are sufficiently large. We considered $4$ layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes. The considered layouts have been plotted and named in Figure \ref{fig:sim_layouts}.
\begin{figure}[htbp]
\begin{center}
    \includegraphics{images/layouts.pdf}
\end{center}
\caption{Layouts Normal Big}
\label{fig:sim_layouts}
\end{figure}
To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with unmodified sensor measurment variances $r_i=5$ metres. Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $f$, thus, $f=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF. The plotted average RMSE of our proposed method as well as that of the unencrypted EIF filter can be seen in Figure \ref{fig:sim_layout_errors}.
\begin{figure}[htbp]
\begin{center}
    \includegraphics{images/layout_errors.pdf}
\end{center}
\caption{Layout errors}
\label{fig:sim_layout_errors}
\end{figure}
From the results it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification in Section \ref{subsec:range_measurement_mod} has almost no effect on the performance when comparied to a normal EIF filter. The robustness of the privacy-preserving method is likely due to the rationality of Assumption \ref{assum:measurement_size}, the relative size of measurements to the sensor variances in our simulations, and the sufficiently large fractional precision.

@@

\section{Conclusion} \label{sec:conclusion}
To develop a model-based localisation algorithm which preserves navigator and sensor privacy, we first defined the novel notion of an LCAO secure encryption scheme and gave a provably secure implementation based on the Joye-Libert aggregation scheme. This scheme was then used in our proposed private EIF, where sensors compute measurement information homomorphically such that it can be privately used by a navigator. Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localisation environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearlity requirements can be applied. Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the relaxing of the Gaussian modified noise assumption and the exploring of implications behind an active sensor attacker model.

>>>>

Recalling Assumption \ref{assum:measurement_size}, modified measurement noise resembles a Gaussian distribution when measurements are sufficiently large. We considered $4$ layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes. The considered layouts have been plotted and named in Figure \ref{fig:sim_layouts}.
\begin{figure}[htbp]
\begin{center}
    \includegraphics{images/layouts.pdf}
\end{center}
\caption{Layouts Normal Big}
\label{fig:sim_layouts}
\end{figure}
To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with unmodified sensor measurement variances $r_i=5$ metres. Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $f$, thus, $f=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF. The plotted average RMSE of our proposed method as well as that of the unencrypted EIF filter can be seen in Figure \ref{fig:sim_layout_errors}.
\begin{figure}[htbp]
\begin{center}
    \includegraphics{images/layout_errors.pdf}
\end{center}
\caption{Layout errors}
\label{fig:sim_layout_errors}
\end{figure}
From the results, it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification in Section \ref{subsec:range_measurement_mod} has almost no effect on the performance when compared to a normal EIF filter. The robustness of the privacy-preserving method is likely due to the rationality of Assumption \ref{assum:measurement_size}, the relative size of measurements to the sensor variances in our simulations, and the sufficiently large fractional precision.

@@

\section{Conclusion} \label{sec:conclusion}
To develop a model-based localisation algorithm which preserves navigator and sensor privacy, we first defined the novel notion of an LCAO secure encryption scheme and gave a provably secure implementation based on the Joye-Libert aggregation scheme. This scheme was then used in our proposed private EIF, where sensors compute measurement information homomorphically such that it can be privately used by a navigator. Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localisation environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearity requirements can be applied. Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the relaxing of the Gaussian modified noise assumption and the exploring of implications behind an active sensor attacker model.
